### 2019-01-26 micro3_3.tex
Micro

However it is not a full equilibrium with transfers. Because in the definition of full equilibrium with transfers instead of (iii) condition is the following:
\begin{align*}
x_i^*\ \text{maximizes } \succsim_i\ \text{ over }B(p) = \left\{x_i \in X_i: px_i \le w_i \right\}\ \forall\ i = 1, \dots, I
\end{align*}
For the 1st consumer his budget set with such a price vector is:
\begin{align*}
\left\{(x_{11}, x_{21})\in X_1:\ (1\ 0)\cdot(x_{11}, x_{21})^T = x_{11} \le w_1 = 0\right\} \equiv \left\{(x_{11}, x_{21})\in X_1:\ x_{11} = 0 \right\}
\end{align*} 
Of course $x_1^*$ does not maximizes hit utility on the aforementioned set: increase of $x_{21}$ could make him strictly better off still remainig in the budget set.
\section*{Problem 6}
\begin{enumerate}[(i)]
	\item Assume by contradiction $\exists\ $ good $l$: $p_l < 0$. By strict monotonicity of preferences $\forall\ \varepsilon >0\ \ \hat{x_i} = x_i^* + \mathbb{I}_l\varepsilon \succ_i x_i^*$ (where $\mathbb{I}_l$ is a vector of zeros with 1 as a $l$-th entry). However 
	\begin{align*}
	p\hat{x_i} = px_i^* + p_l\varepsilon < px_i^* \le w_i
	\end{align*}
	As a result 
	\begin{align*}
	\exists\ \hat{x_i}: \hat{x_i} \succ x_i^*: p\hat{x_i} \le w_i
	\end{align*}
	which violates the definition of quasi equilibrium that means that all entried of p-vector are nonnegative.
	\item By the balanced budget condition:
	\begin{align*}
	\sum_{i=1}^I w_i = p \bar{\omega} + \sum_{j=1}^J py_j^*\\
	\sum_{i=1}^I w_i = p \left(\bar{\omega} + \sum_{j=1}^J y_j\right) > 0
	\end{align*}
	Since $p \ge 0$ and $\left(\bar{\omega} + \sum_{j=1}^J y_j\right) >> 0$. As a result $\sum_{i=1}^I w_i > 0$ hence there exists at least one agent whose wealth is positive.
	\item A buget set of the consumer $i_0$ is:
	\begin{align*}
	B(p, w_{i_0}) = \left\{x_{i_0} \in X_{i_0}: px_{i_0} \le w_{i_0} \right\}
	\end{align*}
	Assume that $x_{i_0} \succ_{i_0} x^*_{i_0}$ and $x_{i_0} \in B(p, w_{i_0})$. By the strictly monotonicity of preferences the only case which is possible is $px_{i_0} = w_{i_0} > 0$. By continuity of preferences both sets:
	\begin{align*}
	U = \left\{x_i \in X_i: x_i \succsim_i x_i^* \right\}\\
	L = \left\{x_i \in X_i: x_i \precsim_i x_i^* \right\}
	\end{align*}
	are closed
	\item Assume by contradiction that there exists some good $l$ such that $p_l \le 0$. Consider $\varepsilon > 0$ and $\hat{x_{i_0}} = x_{i_0}^* + \mathbb{I}_l\varepsilon$. By the strict monotonicity $\hat{x_{i_0}} \succ x_{i_0}^*$ but $p\hat{x_{i_0}} = px_{i_0}^* + p_l\varepsilon \le px_{i_0}^* \le w_{i_0}$ which contradict to the fact that $x_{i_0}^*$ is the preferences maximizer over the budget set. Thus, $p_l > 0\ \forall\ l = 1, \dots, L$. 
	\item $w_i \ge 0, \forall\ i$ because otherwise there cannot exist such an allocation $x_i$ that for $p >> 0$, $px_i \le w_i$ hence there cannot exist any quasi-equilibria which contradicts to the set up of the problem. Then, if $w_i = 0$ then for $p >> 0$ the budget set contains only $x_i^* = 0$ and this point maximizes preferences over such a budget set. In case $w_i > 0$ see (iii). AS a result, a quasi-equilibrium is in fact a full equilibrium.
	\item Without strong monotonicity we would not be able to conclude that $p >> 0$ (actually solution to the problem 5 demonstrate the case when p (as a vector) is not strictly positive (i.e. contains zero elements)). Hence strong monotonicity indeed plays crucial role for the equivalence between notions of quasi- and full equilibria.
\end{enumerate}
\end{document}

>>>>

However it is not a full equilibrium with transfers. Because in the definition of full equilibrium with transfers instead of (iii) condition is the following:
x_i^*\ \text{maximizes } \succsim_i\ \text{ over }B(p) = \left\{x_i \in X_i: px_i \le w_i \right\}\ \forall\ i = 1, \dots, I
For the 1st consumer his budget set with such a price vector is:
\left\{(x_{11}, x_{21})\in X_1:\ (1\ 0)\cdot(x_{11}, x_{21})^T = x_{11} \le w_1 = 0\right\} \equiv \left\{(x_{11}, x_{21})\in X_1:\ x_{11} = 0 \right\}
Of course $x_1^*$ does not maximizes hit utility on the aforementioned set: increase of $x_{21}$ could make him strictly better off still remainig in the budget set.
\section*{Problem 6}
	\item Assume by contradiction $\exists\ $ good $l$: $p_l < 0$. By strict monotonicity of preferences $\forall\ \varepsilon >0\ \ \hat{x_i} = x_i^* + \mathbb{I}_l\varepsilon \succ_i x_i^*$ (where $\mathbb{I}_l$ is a vector of zeros with 1 as a $l$-th entry). However 
	p\hat{x_i} = px_i^* + p_l\varepsilon < px_i^* \le w_i
	As a result 
	\exists\ \hat{x_i}: \hat{x_i} \succ x_i^*: p\hat{x_i} \le w_i
	which violates the definition of quasi equilibrium that means that all entried of p-vector are nonnegative.
	\item By the balanced budget condition:
	\sum_{i=1}^I w_i = p \bar{\omega} + \sum_{j=1}^J py_j^*\\
	\sum_{i=1}^I w_i = p \left(\bar{\omega} + \sum_{j=1}^J y_j\right) > 0
	Since $p \ge 0$ and $\left(\bar{\omega} + \sum_{j=1}^J y_j\right) >> 0$. As a result $\sum_{i=1}^I w_i > 0$ hence there exists at least one agent whose wealth is positive.
	\item A buget set of the consumer $i_0$ is:
	B(p, w_{i_0}) = \left\{x_{i_0} \in X_{i_0}: px_{i_0} \le w_{i_0} \right\}
	Assume that $x_{i_0} \succ_{i_0} x^*_{i_0}$ and $x_{i_0} \in B(p, w_{i_0})$. By the strictly monotonicity of preferences the only case which is possible is $px_{i_0} = w_{i_0} > 0$. Obviously (by strictly monotonicity of preferences) for each positive $\varepsilon$, $x_{\varepsilon} = (1-\varepsilon)x_{i_0} \prec_i x_{i_0}$ and $px_{\varepsilon} < w_{i_0}$. Let us prove that there exists such a small $\varepsilon$ that $x_{i_0}^* \prec_{i_0} x_{\varepsilon} \prec_{i_0} x_{i_0}$. Indeed, assume by contradiction that $\forall\ \varepsilon > 0\ x_{i_0}^* \succsim x_{\varepsilon}$. By continuity of preferences $\lim_{\varepsilon \to 0} x_{\varepsilon} = x_{i_0} \precsim_{i_0} \lim_{\varepsilon \to 0} x_{i_0}^* = x_{i_0}^*$ which contradicts to the fact that $x_{i_0} \succ_{i_0} x_{i_0}^*$. Thus, $\exists\  x_{\varepsilon}: x_{\varepsilon} \succ_{i_0} x_{i_0}^*\text{ and } px_{\varepsilon} < w_{i_0}$. The contradiction to the definition of quasi-equilibrium demonstrates that $x_{i_0}^*$ indeed maximizes preferences over the budget set.
	\item Assume by contradiction that there exists some good $l$ such that $p_l \le 0$. Consider $\varepsilon > 0$ and $\hat{x_{i_0}} = x_{i_0}^* + \mathbb{I}_l\varepsilon$. By the strict monotonicity $\hat{x_{i_0}} \succ x_{i_0}^*$ but $p\hat{x_{i_0}} = px_{i_0}^* + p_l\varepsilon \le px_{i_0}^* \le w_{i_0}$ which contradict to the fact that $x_{i_0}^*$ is the preferences maximizer over the budget set. Thus, $p_l > 0\ \forall\ l = 1, \dots, L$. 
	\item $w_i \ge 0, \forall\ i$ because otherwise there cannot exist such an allocation $x_i$ that for $p >> 0$, $px_i \le w_i$ hence there cannot exist any quasi-equilibria which contradicts to the set up of the problem. Then, if $w_i = 0$ then for $p >> 0$ the budget set contains only $x_i^* = 0$ and this point maximizes preferences over such a budget set. In case $w_i > 0$ see (iii). As a result, a quasi-equilibrium is in fact a full equilibrium.
	\item Without strong monotonicity we would not be able to conclude that $p >> 0$ (actually solution to the problem 5 demonstrates the case when $p$ (as a vector) is not strictly positive (i.e. contains zero elements)). Hence strong monotonicity indeed plays crucial role for the equivalence between notions of quasi- and full equilibria.
\end{document}
